Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-06-29 manuscript/supplement_motifs.tex

>>>>

    \begin{figure}
        \centering
        \includegraphics{figures/persistence_positions_Apparent.eps}
        \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Here we show the relationships between persistence and the proportions of the three positions in the apparent competition motif at three levels of probability of extinction for basal resources (p=0.1, 0.26, and 0.42), indicated by line colour. Line style indicates the motif  position. }
        \label{fig:apparent_positions}
    \end{figure}

    \begin{figure}
        \centering
        \includegraphics{figures/persistence_positions_Direct.eps}
        \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Here we show the relationships between persistence and the proportions of the three positions in the direct competition motif at three levels of probability of extinction for basal resources (p=0.1, 0.26, and 0.42), indicated by line colour. Line style indicates the motif  position. }
        \label{fig:direct_positions}
    \end{figure}

    \begin{figure}
        \centering
        \includegraphics{figures/persistence_positions_Three-species.eps}
        \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Here we show the relationships between persistence and the proportions of the three positions in the three-species chain motif at three levels of probability of extinction for basal resources (p=0.1, 0.26, and 0.42), indicated by line colour. Line style indicates the motif  position. }
        \label{fig:chain_positions}
    \end{figure}
